Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-11-28 paper/paper.tex
Tweak refs + Move Box1 + Change Box numbers

\title{Dark Control:\\
       A Unified Account of Default Mode Function\\
       by Markov Decision Processes}

@@

\begin{mdframed}
  \vspace{1em}
  \textbf{Box 1: Hypotheses for testing the MDP account of DMN function}
\begin{enumerate}
\item Experiment (Humans): We hypothesize a functional relationship between the DMN closely associated with the occurrence of stimulus-independent thoughts and the reward circuitry. During an iterative neuroeconomic two-player game, fMRI signals in the DMN could be used to predict reward-related signals in the nucleus accumbens across trials in a continuous learning paradigms. We expect that the more DMN activity is measured to be increased, supposedly the higher the tendency for stimulus-independent thoughts, and the more the fMRI signals in the reward circuits should be independent of the reward context
in the sensory environment.

@@

\begin{mdframed}
% neuroscience of Bellman equation
  \vspace{2em}
  \textbf{Box 2: Neural correlates of the Bellman equation in the DMN}
% \hspace{-1.5em}
Relating decomposition of consecutive action choices by the Bellman equation
to neuroscience,
specific neural activity in the dorsal prefrontal cortex (BA9)
was linked to processing ``goal-tree sequences''
in human neuroimaging experiments
\citep{koechlin1999role, koechlin2000dissociating}.
Sub-goal exploration may require multi-task switching
between cognitive processes
as later parts of a solution
frequently depend on respective earlier steps in a given solution path, which
necessitates storage of expected intermediate outcomes.
As such,
``cognitive branching'' operations for nested processing of behavioral strategies
are likely to
entail secondary reallocation of attention and working-memory resources.
Further neuroimaging experiments \citep{braver2002role} corroborated
the prefrontal DMN to subserve
``processes related to the management and monitoring of sub-goals while maintaining information in working memory''.
%
Moreover,
neurological patients with lesions in this DMN region were reported
to be impaired in aspects of realizing ``multiple sub-goal scheduling''
\citep{burgess2000cognitive}.
Hence,
the various advanced human mental abilities subserved by the DMN, such as
planning and abstract reasoning, can be viewed to involve some form of
action-decision branching to enable higher-order executive control.
\end{mdframed}

@@

>>>>

\title{Dark Control:\\
       Towards a Unified Account of Default Mode Function\\
       by Markov Decision Processes}

@@

@@

\begin{mdframed}
% neuroscience of Bellman equation
  \vspace{2em}
  \textbf{Box 1: Neural correlates of the Bellman equation in the DMN}
% \hspace{-1.5em}
Relating decomposition of consecutive action choices by the Bellman equation
to neuroscience,
specific neural activity in the dorsal prefrontal cortex (BA9)
was linked to processing ``goal-tree sequences''
in human neuroimaging experiments
\citep{koechlin1999role, koechlin2000dissociating}.
Sub-goal exploration may require multi-task switching
between cognitive processes
as later parts of a solution
frequently depend on respective earlier steps in a given solution path, which
necessitates storage of expected intermediate outcomes.
As such,
``cognitive branching'' operations for nested processing of behavioral strategies
are likely to
entail secondary reallocation of attention and working-memory resources.
Further neuroimaging experiments \citep{braver2002role} corroborated
the prefrontal DMN to subserve
``processes related to the management and monitoring of sub-goals while maintaining information in working memory''.
%
Moreover,
neurological patients with lesions in this DMN region were reported
to be impaired in aspects of realizing ``multiple sub-goal scheduling''
\citep{burgess2000cognitive}.
Hence,
the various advanced human mental abilities subserved by the DMN, such as
planning and abstract reasoning, can be viewed to involve some form of
action-decision branching to enable higher-order executive control.
\end{mdframed}

@@

\begin{mdframed}
  \vspace{1em}
  \textbf{Box 2: Hypotheses for testing the MDP account of DMN function}
\begin{enumerate}
\item Experiment (Humans): We hypothesize a functional relationship between the DMN closely associated with the occurrence of stimulus-independent thoughts and the reward circuitry. During an iterative neuroeconomic two-player game, fMRI signals in the DMN could be used to predict reward-related signals in the nucleus accumbens across trials in a continuous learning paradigms. We expect that the more DMN activity is measured to be increased, supposedly the higher the tendency for stimulus-independent thoughts, and the more the fMRI signals in the reward circuits should be independent of the reward context
in the sensory environment.
